AusTraits -- a curated plant trait database for the Australian flora

### 2020-11-10 ms.Rmd
Better citation formatting

---
title: "AusTraits -- a curated plant trait database for the Australian flora"
editor_options:
  chunk_output_type: console
output:
  pdf_document:
    latex_engine: xelatex
    citation_package: natbib
    keep_tex: true
    keep_md: true
biblio-style: naturemag
header-includes:
- \usepackage{inputenc}
#- \usepackage[T1]{fontenc}
- \usepackage{float}
- \usepackage{fontspec}
- \usepackage{unicode-math}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{colortbl}
- \usepackage{lscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
bibliography: [data/references.bib]

>>>>

---
title: "AusTraits -- a curated plant trait database for the Australian flora"
editor_options:
  chunk_output_type: console
output:
  pdf_document:
    latex_engine: xelatex
    citation_package: natbib
    keep_tex: true
    keep_md: true
biblio-style: naturemag
header-includes:
- \usepackage{inputenc}
- \usepackage{float}
- \usepackage{fontspec}
- \usepackage{unicode-math}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{colortbl}
- \usepackage{lscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage[square,sort,comma,numbers]{natbib}
bibliography: [data/references.bib]
